Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-09 paper/main.tex
Updates

Figure~\ref{fig:intro} highlights some of these issues. When constructing DAGs
manually, it is important to test how consistent our DAG is to our dataset. One
of the methods for checking the consistency is by testing whether the implied
CIs of the DAG hold in the dataset or not \citep{Ankan2021}. As each pair of
variables that do not have an edge between them in the DAG implies a CI
statement, we can use a statistical test to check whether that statement holds
in our dataset or not. If we find any violations we can also modify our DAG
based on this and utilizing our domain knowledge to find a suitable orientation
for the edge between the pair of variables.

>>>>

Figure~\ref{fig:intro} highlights some of these issues. Constructing DAG
manually, on the other hand, can also be error prone as it can be difficult to
distinguish various scenarios such as direct or indirect effects, mediation,
and so on. This makes it important to test the consistency of our DAG against
our dataset. One of the methods for testing this is to check whether the
implied CIs of the DAG hold in the dataset or not \citep{Ankan2021}. Each pair
of variables with a missing edge between them in the DAG implies a CI
statement, we can use a statistical test to check whether the statement holds
in our dataset or not. If we find any violations we can also modify our DAG
based on this and utilizing our domain knowledge to find a suitable orientation
for the edge between the pair of variables.
